Supplementary Information to "Improving Models to Predict Holocellulose and Klason Lignin Contents for Peat Soil Organic Matter with Mid Infrared Spectra

### 2022-03-03 analysis/paper/004-paper-m-reduce-underfitting.Rmd
Update manuscript 1, update formatting fo references.

```{r m-reduce-underfitting-5-1}
# compute loos
m1.7_loo <- loo(m1.7, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-5-2}
m1.8_loo <- loo(m1.8, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-5-3}
m1.9_loo <- loo(m1.9, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-5-4}
m1.10_loo <- loo(m1.10, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-5-5}
m1.11_loo <- loo(m1.11, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-6-1}
# compute loos
m2.7_loo <- loo(m2.7, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-6-2}
m2.8_loo <- loo(m2.8, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-6-3}
m2.9_loo <- loo(m2.9, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-6-4}
m2.10_loo <- loo(m2.10, reloo = TRUE, cores = chains)
```

```{r m-reduce-underfitting-6-5}
m2.11_loo <- loo(m2.11, reloo = TRUE, cores = chains)
```

@@

## create table for printing

# holocellulose
loo_comparison_hol <-
  loo_comparison %>%
  dplyr::filter(variably_y == "Holocellulose") %>%
  dplyr::pull(loo_comparison) %>%
  as.data.frame() %>%
  dplyr::select(1:3) %>%
  dplyr::mutate(dplyr::across(dplyr::everything(), round, 1)) %>%
  dplyr::mutate(
    y_variable = "Holocellulose",
    model_code = rownames(.),
    bin_width = c(50, 100, 30, 10, rep("-", 4), 20),
    family = c(rep("Beta", 7), "Gaussian", "Beta"),
    original_model = c(rep(FALSE, 6), TRUE, TRUE, FALSE),
    prior_scale = c(rep("-", 4), 0.5, 2.5, 2.5, 2.5, "-"),
    variables = ifelse(bin_width == "-", "peaks", "bins")
  )

# Klason lignin
loo_comparison_kl <-
  loo_comparison %>%
  dplyr::filter(variably_y == "Klason lignin") %>%
  dplyr::pull(loo_comparison) %>%
  as.data.frame() %>%
  dplyr::select(1:3) %>%
  dplyr::mutate(dplyr::across(dplyr::everything(), round, 1)) %>%
  dplyr::mutate(
    y_variable = "Klason lignin",
    model_code = rownames(.),
    bin_width = c(10, rep("-", 4), 30, 20, 100, 50),
    family = c(rep("Beta", 3), "Gaussian", rep("Beta", 5)),
    original_model = c(rep(FALSE, 3), TRUE, TRUE, rep(FALSE, 4)),
    prior_scale = c("-", 0.5, 2.5, 2.5, 2.5, rep("-", 4)),
    variables = ifelse(bin_width == "-", "peaks", "bins")
  )

@@

# bin width: 50
d_peat_bin50_scale <-
  d_underfitting_flat[[4]] %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(center = TRUE, scale = TRUE)

d_peat_bin50_scale <-
  tibble::tibble(
    center = attr(d_peat_bin50_scale, "scaled:center"),
    scale = attr(d_peat_bin50_scale, "scaled:scale")
  )

d_peat_bin50_flat <-
  d_peat %>%
  ir::ir_bin(width = 50) %>%
  ir::ir_flatten()

d_peat_bin50 <- 
  d_peat_bin50_flat %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(
    center = d_peat_bin50_scale$center, 
    scale = d_peat_bin50_scale$scale
  ) %>%
  as.data.frame()

@@

# predictions
d_peat_pred_best <- 
  dplyr::bind_rows(
    m1.10 %>%
      rstanarm::posterior_predict(newdata = d_peat_bin50) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose"
      ),
    m1.6 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Holocellulose"
      ),
    m1.2 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Holocellulose"
      ),
    m2.2 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Klason lignin"
      ),
    m2.7 %>%
      rstanarm::posterior_predict(newdata = d_peat_bin10) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Klason lignin"
      ),
    m2.6 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:6, function(x) {
      tibble::tibble(
        sample_id = d_peat$sample_id, 
        core_label = d_peat$core_label,
        sampling_longitude = d_peat$sampling_longitude, 
        sampling_latitude = d_peat$sampling_latitude, 
        sampling_altitude = d_peat$sampling_altitude, 
        sample_depth_lower = d_peat$sample_depth_lower, 
        sample_depth_upper = d_peat$sample_depth_upper
      )
    })
  )

@@

# data frame to compare fitted with measured values across all models
d_fitted_comparison <-
  dplyr::bind_rows(
    tibble::tibble(
      y = 
        d %>% 
        dplyr::filter(sample_type != "old magazines") %>% 
        dplyr::pull(hol) %>%
        rep(4),
      yhat = 
        list(m1.2, m1.5, m1.10) %>%
        purrr::map(function(x) {
          apply(posterior_predict(x), 2, median)
        }) %>%
        unlist() %>%
        c(m1.1 %>% predict(type = "response")),
      model = rep(c("Original", "Best all peaks", "Best binned spectra", "Original non-Bayesian"), 
                  each = d %>% dplyr::filter(sample_type != "old magazines") %>% nrow()),
      y_variable = "Holocellulose"
    ),
    tibble::tibble(
      y = 
        d %>% 
        dplyr::filter(sample_type != "office paper") %>% 
        dplyr::pull(kl) %>%
        rep(4),
      yhat = 
        list(m2.2, m2.6, m2.7) %>%
        purrr::map(function(x) {
          apply(posterior_predict(x), 2, median)
        }) %>%
        unlist() %>%
        c(m2.1 %>% predict(type = "response")),
      model = rep(c("Original", "Best all peaks", "Best binned spectra", "Original non-Bayesian"), 
                  each = d %>% dplyr::filter(sample_type != "office paper") %>% nrow()),
      y_variable = "Klason lignin"
    )
  )
```

@@

# bin width: 50
d_veg_bin50_flat <-
  d_veg %>%
  ir::ir_bin(width = 50) %>%
  ir::ir_flatten()

d_veg_bin50 <- 
  d_veg_bin50_flat %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(center = d_peat_bin50_scale$center, 
        scale = d_peat_bin50_scale$scale) %>%
  as.data.frame()

@@

# predictions
d_veg_pred_best <- 
  dplyr::bind_rows(
    m1.10 %>%
      rstanarm::posterior_predict(newdata = d_veg_bin50) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose"
      ),
    m1.6 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Holocellulose"
      ),
    m1.2 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Holocellulose"
      ),
    m2.2 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Klason lignin"
      ),
    m2.7 %>%
      rstanarm::posterior_predict(newdata = d_veg_bin10) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Klason lignin"
      ),
    m2.6 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:6, function(x) {
      tibble::tibble(
        sample_id = d_veg$sample_id, 
        site_name = d_veg$site_name,
        species_name = d_veg$species_name,
        plant_part = d_veg$plant_part
      )
    })
  )

>>>>

```{r m-reduce-underfitting-5-1}
# compute loos
m1.7_loo <- loo(m1.7, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-5-2}
m1.8_loo <- loo(m1.8, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-5-3}
m1.9_loo <- loo(m1.9, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-5-4}
m1.10_loo <- loo(m1.10, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-5-5}
m1.11_loo <- loo(m1.11, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-6-1}
# compute loos
m2.7_loo <- loo(m2.7, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-6-2}
m2.8_loo <- loo(m2.8, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-6-3}
m2.9_loo <- loo(m2.9, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-6-4}
m2.10_loo <- loo(m2.10, reloo = TRUE, cores = chains, recompile = FALSE)
```

```{r m-reduce-underfitting-6-5}
m2.11_loo <- loo(m2.11, reloo = TRUE, cores = chains, recompile = FALSE)
```

@@

## create table for printing
loo_comparison_code <-
  tibble::tibble(
    model_code = paste0("m1.", c(2, 3, 5:11)),
    bin_width = c(rep("-", 4), 10, 20, 30, 50, 100),
    family = c("Gaussian", rep("Beta", 8)),
    original_model = c(rep(TRUE, 2), rep(FALSE, 7)),
    prior_scale = c(rep(2.5, 3), 0.5, rep("-", 5)),
    variables = ifelse(bin_width == "-", "peaks", "bins")
  )

# holocellulose
loo_comparison_hol <-
  loo_comparison %>%
  dplyr::filter(variably_y == "Holocellulose") %>%
  dplyr::pull(loo_comparison) %>%
  as.data.frame() %>%
  dplyr::select(1:3) %>%
  dplyr::mutate(model_code = rownames(.)) %>%
  dplyr::mutate(dplyr::across(1:3, round, 1)) %>%
  dplyr::left_join(loo_comparison_code, by = "model_code")

# Klason lignin
loo_comparison_kl <-
  loo_comparison %>%
  dplyr::filter(variably_y == "Klason lignin") %>%
  dplyr::pull(loo_comparison) %>%
  as.data.frame() %>%
  dplyr::select(1:3) %>%
  dplyr::mutate(model_code = rownames(.)) %>%
  dplyr::mutate(dplyr::across(1:3, round, 1)) %>%
  dplyr::left_join(
    loo_comparison_code %>%
      dplyr::mutate(model_code =
                      model_code %>% stringr::str_replace(pattern = "^m1", replacement = "m2")), 
    by = "model_code")

@@

# bin width: 20
d_peat_bin20_scale <-
  d_underfitting_flat[[2]] %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(center = TRUE, scale = TRUE)

d_peat_bin20_scale <-
  tibble::tibble(
    center = attr(d_peat_bin20_scale, "scaled:center"),
    scale = attr(d_peat_bin20_scale, "scaled:scale")
  )

d_peat_bin20_flat <-
  d_peat %>%
  ir::ir_bin(width = 20) %>%
  ir::ir_flatten()

d_peat_bin20 <- 
  d_peat_bin20_flat %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(
    center = d_peat_bin20_scale$center, 
    scale = d_peat_bin20_scale$scale
  ) %>%
  as.data.frame()

@@

# predictions
d_peat_pred_best <- 
  dplyr::bind_rows(
    m1.8 %>%
      rstanarm::posterior_predict(newdata = d_peat_bin20) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose"
      ),
    m1.6 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Holocellulose"
      ),
    m1.2 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Holocellulose"
      ),
    m2.2 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Klason lignin"
      ),
    m2.8 %>%
      rstanarm::posterior_predict(newdata = d_peat_bin20) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Klason lignin"
      ),
    m2.6 %>%
      rstanarm::posterior_predict(newdata = d_peat_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:6, function(x) {
      tibble::tibble(
        sample_id = d_peat$sample_id, 
        core_label = d_peat$core_label,
        sampling_longitude = d_peat$sampling_longitude, 
        sampling_latitude = d_peat$sampling_latitude, 
        sampling_altitude = d_peat$sampling_altitude, 
        sample_depth_lower = d_peat$sample_depth_lower, 
        sample_depth_upper = d_peat$sample_depth_upper
      )
    })
  )

@@

# data frame to compare fitted with measured values across all models
d_fitted_comparison <-
  dplyr::bind_rows(
    tibble::tibble(
      y = 
        d %>% 
        dplyr::filter(sample_type != "old magazines") %>% 
        dplyr::pull(hol) %>%
        rep(4),
      yhat = 
        list(m1.2, m1.5, m1.8) %>%
        purrr::map(function(x) {
          apply(posterior_predict(x), 2, median)
        }) %>%
        unlist() %>%
        c(m1.1 %>% predict(type = "response")),
      model = rep(c("Original", "Best all peaks", "Best binned spectra", "Original non-Bayesian"), 
                  each = d %>% dplyr::filter(sample_type != "old magazines") %>% nrow()),
      y_variable = "Holocellulose"
    ),
    tibble::tibble(
      y = 
        d %>% 
        dplyr::filter(sample_type != "office paper") %>% 
        dplyr::pull(kl) %>%
        rep(4),
      yhat = 
        list(m2.2, m2.6, m2.8) %>%
        purrr::map(function(x) {
          apply(posterior_predict(x), 2, median)
        }) %>%
        unlist() %>%
        c(m2.1 %>% predict(type = "response")),
      model = rep(c("Original", "Best all peaks", "Best binned spectra", "Original non-Bayesian"), 
                  each = d %>% dplyr::filter(sample_type != "office paper") %>% nrow()),
      y_variable = "Klason lignin"
    )
  )
```

@@

# bin width: 50
d_veg_bin20_flat <-
  d_veg %>%
  ir::ir_bin(width = 20) %>%
  ir::ir_flatten()

d_veg_bin20 <- 
  d_veg_bin20_flat %>%
  dplyr::select(-1) %>%
  t() %>%
  as.data.frame() %>%
  scale(center = d_peat_bin20_scale$center, 
        scale = d_peat_bin20_scale$scale) %>%
  as.data.frame()

@@

# predictions
d_veg_pred_best <- 
  dplyr::bind_rows(
    m1.8 %>%
      rstanarm::posterior_predict(newdata = d_veg_bin20) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose"
      ),
    m1.6 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Holocellulose"
      ),
    m1.2 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Holocellulose"
      ),
    m2.2 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Original",
        variable_y = "Klason lignin"
      ),
    m2.8 %>%
      rstanarm::posterior_predict(newdata = d_veg_bin20) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Klason lignin"
      ),
    m2.6 %>%
      rstanarm::posterior_predict(newdata = d_veg_res) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best all peaks",
        variable_y = "Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:6, function(x) {
      tibble::tibble(
        sample_id = d_veg$sample_id, 
        site_name = d_veg$site_name,
        species_name = d_veg$species_name,
        plant_part = d_veg$plant_part
      )
    })
  )

### 2022-03-03 analysis/paper/005-paper-m-minerals.Rmd
Update manuscript 1, update formatting fo references.

brms_beta_priors2 <-
  c(
    brms::prior_string(paste0("horseshoe(df = 1, scale_global = ", prior_hs_tau0[[4]], ", df_global = 1, autoscale = TRUE)"),
                       class = "b"),
    brms::prior_string("normal(0, 2.5)", class = "Intercept"),
    brms::prior_string("gamma(0.01, 0.01)", class = "phi")
  )

m1.13 <- 
  brms::brm(
    hol ~ ., 
    data = 
      d_underfitting[[4]] %>% 
      dplyr::select(-kl),
    family = Beta(link = "logit", link_phi = "log"),
    prior = brms_beta_priors2,
    cores = chains,
    chains = chains,
    warmup = warmup,
    iter = iter,
    seed = seed,
    control = list(adapt_delta = 0.99, max_treedepth = 15) # with default adapt_delta (0.8): 22 divergent transitions; adapt_delta = 0.99: There were 2000 transitions after warmup that exceeded the maximum treedepth. Increase max_treedepth above 10
  ) 
```

@@

```{r m-minerals-3}
# plot of fitted values against measured values
d_minerals_pred <-
  tibble::tibble(
    fit = c(
      posterior_predict(m1.2, newdata = d) %>%
        apply(2, median),
      posterior_predict(m1.10, newdata = d_underfitting[[4]]) %>%
        apply(2, median),
      posterior_predict(m1.6, newdata = d) %>%
        apply(2, median),
      posterior_predict(m1.12) %>%
        apply(2, median),
      posterior_predict(m1.13) %>%
        apply(2, median)
    ),
    model = 
      rep(c("Original", "Binned (no minerals)", "Peaks (no minerals)", "Peaks", "Binned"), each = nrow(d)) %>%
      factor(levels = c("Original", "Peaks (no minerals)", "Binned (no minerals)", "Peaks", "Binned"))
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:5, function(x) {
      d %>% 
        dplyr::select(sample_type, hol) %>%
        dplyr::mutate(mineral = ifelse(sample_type == "old magazines", TRUE, FALSE))
    })
  )

@@

# Holocellulose
m1.10_pars <- 
  m1.10 %>%
  as.data.frame() %>%
  dplyr::select(dplyr::contains("b_V"))

m1.10_pars <- 
  m1.10_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m1.10_pars),
    wn = d_underfitting_flat[[4]]$x,
    variable_y = "Holocellulose (no minerals)"
  )

@@

m1.13_pars <- 
  m1.13_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m1.13_pars),
    wn = d_underfitting_flat[[4]]$x,
    variable_y = "Holocellulose (with minerals)"
  )

# Klason lignin
m2.7_pars <- 
  m2.7 %>%
  as.data.frame() %>%
  dplyr::select(dplyr::contains("b_V"))

m2.7_pars <- 
  m2.7_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m2.7_pars),
    wn = d_underfitting_flat[[1]]$x,
    variable_y = "Klason lignin"
  )

# combine
m_pars <-
  dplyr::bind_rows(
    m1.10_pars,
    m1.13_pars,
    m2.7_pars
  )

>>>>

brms_beta_priors2 <-
  c(
    brms::prior_string(paste0("horseshoe(df = 1, scale_global = ", prior_hs_tau0[[2]], ", df_global = 1, autoscale = TRUE)"),
                       class = "b"),
    brms::prior_string("normal(0, 2.5)", class = "Intercept"),
    brms::prior_string("gamma(0.01, 0.01)", class = "phi")
  )

m1.13 <- 
  brms::brm(
    hol ~ ., 
    data = 
      d_underfitting[[2]] %>% 
      dplyr::select(-kl),
    family = Beta(link = "logit", link_phi = "log"),
    prior = brms_beta_priors2,
    cores = chains,
    chains = chains,
    warmup = warmup,
    iter = iter,
    seed = seed,
    control = list(adapt_delta = 0.99, max_treedepth = 15)
  ) 
```

@@

```{r m-minerals-3}
# plot of fitted values against measured values
d_minerals_pred <-
  tibble::tibble(
    fit = c(
      posterior_predict(m1.2, newdata = d) %>%
        apply(2, median),
      posterior_predict(m1.8, newdata = d_underfitting[[2]]) %>%
        apply(2, median),
      posterior_predict(m1.6, newdata = d) %>%
        apply(2, median),
      posterior_predict(m1.12) %>%
        apply(2, median),
      posterior_predict(m1.13) %>%
        apply(2, median)
    ),
    model = 
      rep(c("Original", "Binned (no minerals)", "Peaks (no minerals)", "Peaks", "Binned"), each = nrow(d)) %>%
      factor(levels = c("Original", "Peaks (no minerals)", "Binned (no minerals)", "Peaks", "Binned"))
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1:5, function(x) {
      d %>% 
        dplyr::select(sample_type, hol) %>%
        dplyr::mutate(mineral = ifelse(sample_type == "old magazines", TRUE, FALSE))
    })
  )

@@

# Holocellulose
m1.8_pars <- 
  m1.8 %>%
  as.data.frame() %>%
  dplyr::select(dplyr::contains("b_V"))

m1.8_pars <- 
  m1.8_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m1.8_pars),
    wn = d_underfitting_flat[[2]]$x,
    variable_y = "Holocellulose (no minerals)"
  )

@@

m1.13_pars <- 
  m1.13_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m1.13_pars),
    wn = d_underfitting_flat[[2]]$x,
    variable_y = "Holocellulose (with minerals)"
  )

# Klason lignin
m2.8_pars <- 
  m2.8 %>%
  as.data.frame() %>%
  dplyr::select(dplyr::contains("b_V"))

m2.8_pars <- 
  m2.8_pars %>%
  purrr::map_df(function(x) {
    res <- quantile(x, c(0.5, 0.05, 0.95))
    tibble::tibble(
      median = res[[1]],
      lwr = res[[2]],
      upr = res[[3]]
    )
  }) %>%
  dplyr::mutate(
    par_name = colnames(m2.8_pars),
    wn = d_underfitting_flat[[2]]$x,
    variable_y = "Klason lignin"
  )

# combine
m_pars <-
  dplyr::bind_rows(
    m1.8_pars,
    m1.13_pars,
    m2.8_pars
  )
